Certified Symbolic Finite Transducers: Formalization and Applications to String Manipulation

### 2025-07-23 Paper/main.tex
add paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lstset{
	basicstyle=\ttfamily,
	keywordstyle=\color{blue}\bfseries,
	keywords={definition,if,then,else, where, record, fun, lemma, type_synonym, fixes, shows, assumes, shows},
	escapeinside={|}{|}
}

@@

\begin{figure}[hbt!]
	\begin{lstlisting}
definition subtrans_comp where
"subtrans_comp M q |$\alpha$| f q|$'$| F fe T D1 D2 =
 FOREACH {t.t|$\in$|T} (|$\lambda$| (q1,|$\alpha'$|,q1|$'$|) (D1,D2).
  (if (nemptyIs (intersectIs |$\alpha$| |$\alpha'$|)) then
    do {
      D1 |$\leftarrow$| 
       (if (F (M f) (intersectIs |$\alpha$| |$\alpha'$|)) 
          |$\neq$| None) then
         let |$\alpha_i$| = the (F (M f) 
              (intersectIs |$\alpha$| |$\alpha'$|)) in
         RETURN {((q,q1), |$\alpha_i$|, (q|$'$|,q1|$'$|))} 
                |$\cup$| D1
        else RETURN D1);
      D2 |$\leftarrow$| 
       (if fe (M f) (intersectIs |$\alpha$| |$\alpha'$|) 
        then 
         RETURN {((q,q1), (q|$'$|,q1|$'$|))} |$\cup$| D2 
        else RETURN D2);
      RETURN (D1, D2) }
   else (RETURN (D1, D2)))) (D1, D2)"
    \end{lstlisting}
    \caption{The computation of \texttt{subtrans\_comp}}
    \label{fig-def-subtrans_comp}
    \end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lstdefinelanguage{Isabelle}{
    keywords={definition,theorem,lemma,proof,qed,by,auto,simp,apply,done,
              where,fixes,assumes,shows,if,then,else,let,in,case,of,
              record,datatype,type_synonym,fun,function,primrec},
    sensitive=true,
    morecomment=[s]{(*}{*)},
    morestring=[b]",
  }

\lstset{
  language=Isabelle,
	basicstyle=\ttfamily,
	keywordstyle=\color{blue}\bfseries,
	morekeywords={definition,if,then,else,where,record,fun,lemma,type_synonym,fixes,shows,assumes,and},
	escapeinside={|}{|},
  sensitive=true
}

@@

\begin{figure}[hbt!]
\begin{lstlisting}[language=SMTLIB]
definition subtrans_comp where
"subtrans_comp M q |$\alpha$| f q|$'$| F fe T D1 D2 =
 FOREACH {t.t|$\in$|T} (|$\lambda$| (q1,|$\alpha'$|,q1|$'$|) (D1,D2).
  (if (nemptyIs (intersectIs |$\alpha$| |$\alpha'$|)) then
    do {
      D1 |$\leftarrow$| 
       (if (F (M f) (intersectIs |$\alpha$| |$\alpha'$|)) 
          |$\neq$| None) then
         let |$\alpha_i$| = the (F (M f) 
              (intersectIs |$\alpha$| |$\alpha'$|)) in
         RETURN {((q,q1), |$\alpha_i$|, (q|$'$|,q1|$'$|))} 
                |$\cup$| D1
        else RETURN D1);
      D2 |$\leftarrow$| 
       (if fe (M f) (intersectIs |$\alpha$| |$\alpha'$|) 
        then 
         RETURN {((q,q1), (q|$'$|,q1|$'$|))} |$\cup$| D2 
        else RETURN D2);
      RETURN (D1, D2) }
   else (RETURN (D1, D2)))) (D1, D2)"
    \end{lstlisting}
    \caption{The computation of \texttt{subtrans\_comp}}
    \label{fig-def-subtrans_comp}
    \end{figure}
